curling

### 2020-08-02 inst/curling.Rmd
slightly more efficient idiom
clarification

Thus we see that Canada came first in 1998, third in 2002, and so on;
in 1998, Canada came first, China did not compete [`NA` meaning did
not compete], Denmark came second, and so on.

@@

```{r,definsupportb,cache=TRUE}
H1 <- ordertable2supp(ranktable_to_ordertable(wikitable_to_ranktable(ct)))
H1
mH1 <- maxp(H1)
pie(mH1)
```

>>>>

Thus the first row shows that Canada came first in 1998, third in
2002, and so on; the first column shows that in 1998, Canada came
first, China did not compete [`NA` meaning did not compete], Denmark
came second, and so on.

@@

```{r,definsupportb,cache=TRUE}
H1 <- ordertable2supp(ct)
H1
mH1 <- maxp(H1)
pie(mH1)
```
